On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-04-15 MS.tex
Tick on the INSIDE of the axis Reference: dryad added

Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}. Data were also deposited in the Dryad repository:

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait. Traits are: $A_{area}$ (or $A_{mass}$) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, $H_{max}$ = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, $NAR_{area}$  (or $NAR_{mass}$) = net mass assimilation rate per unit of leaf area (or leaf mass), $N_{mass}$ (or $N_{area}$) = nitrogen content per unit of leaf mass (or leaf area), $P_{mass}$ = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}

>>>>

Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}. The dataset is in open access \citep{Gibert:2016}.

@@

The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}. Data available from the Dryad Digital Repository: \smurl{http://dx.doi.org/10.5061/dryad.701q8}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait. Traits are: $A_{area}$ (or $A_{mass}$) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, $H_{max}$ = asymptotic or maximum height, Ks = stem hydraulic conductance, LAR = leaf area ratio, LMR = leaf mass ratio, $NAR_{area}$  (or $NAR_{mass}$) = net mass assimilation rate per unit of leaf area (or leaf mass), $N_{mass}$ (or $N_{area}$) = nitrogen content per unit of leaf mass (or leaf area), $P_{mass}$ = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}
